Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2024-07-31 paper.qmd
repositioned tsne_30 img

## Add arrows
arrow_df_pbmc <- tibble(x = c(94, 245, 101, 150),
             xend = c(96, 263, 98, 180),
             y = c(10.06, 9.72, 9.88, 9.855),
             yend = c(10.14, 9.8, 9.85, 10))

error_plot_pbmc <- ggplot(error_pbmc, 
                              aes(x = b_non_empty, 
                                  y = log(Error), 
                                  colour = method)) + 
  geom_point(size = 0.8) +
  geom_line(linewidth = 0.3) + 
  geom_vline(xintercept = 135, linetype="solid", 
             color = "black", linewidth=0.8, alpha = 0.5) +
  scale_color_manual(values=c('#e41a1c','#377eb8','#4daf4a','#ff7f00',
                              '#984ea3','#999999','#a65628','#f781bf')) +
  ylab("log(absolute error)") +
  xlab("number of non-empty bins")+
    geom_segment(data = arrow_df_pbmc, aes(
      x = x,  
      y = y,  
      xend = xend, 
      yend = yend), 
      arrow = arrow(length = unit(0.01, "npc"),
        ends = "first"), 
        color = "black") +
    inset_element(p = tsne_5_img, 
                  left = 1.7, 
                  bottom = 0.16, 
                  right = 0, 
                  top = 0.31) +                   
    inset_element(p = phate_5_img, 
                  left = 0.6, 
                  bottom = 0.5, 
                  right = 0, 
                  top = 0.65) +                   
    inset_element(p = umap_img, 
                  left = 1.3, 
                  bottom = 0.3, 
                  right = 0, 
                  top = 0.5) +
    inset_element(p = tsne_30_img, 
                  left = 0.6, 
                  bottom = 0.03, 
                  right = 0, 
                  top = 0.23) +
  theme(#aspect.ratio = 0.75,
        axis.text.x = element_text(size = 7),
        axis.text.y = element_text(size = 7),
        axis.title.x = element_text(size = 7),
        axis.title.y = element_text(size = 7, angle = 90),
        legend.position = "none",
        legend.text = element_text(size = 7))

>>>>

## Add arrows
arrow_df_pbmc <- tibble(x = c(94, 245, 105, 150),
             xend = c(96, 263, 94, 180),
             y = c(10.06, 9.72, 9.88, 9.855),
             yend = c(10.14, 10, 9.79, 10))

error_plot_pbmc <- ggplot(error_pbmc, 
                              aes(x = b_non_empty, 
                                  y = log(Error), 
                                  colour = method)) + 
  geom_point(size = 0.8) +
  geom_line(linewidth = 0.3) + 
  geom_vline(xintercept = 135, linetype="solid", 
             color = "black", linewidth=0.8, alpha = 0.5) +
  scale_color_manual(values=c('#e41a1c','#377eb8','#4daf4a','#ff7f00',
                              '#984ea3','#999999','#a65628','#f781bf')) +
  ylab("log(absolute error)") +
  xlab("number of non-empty bins")+
    geom_segment(data = arrow_df_pbmc, aes(
      x = x,  
      y = y,  
      xend = xend, 
      yend = yend), 
      arrow = arrow(length = unit(0.01, "npc"),
        ends = "first"), 
        color = "black") +
  theme(#aspect.ratio = 0.75,
        axis.text.x = element_text(size = 7),
        axis.text.y = element_text(size = 7),
        axis.title.x = element_text(size = 7),
        axis.title.y = element_text(size = 7, angle = 90),
        legend.position = "bottom",
        legend.text = element_text(size = 7),
        legend.key.height = unit(0.3, 'cm'),
        legend.key.width = unit(0.3, 'cm'),
        legend.key.size = unit(3, 'cm')) +
    inset_element(p = tsne_5_img, 
                  left = 1.7, 
                  bottom = 0.16, 
                  right = 0, 
                  top = 0.31) +                   
    inset_element(p = phate_5_img, 
                  left = 0.6, 
                  bottom = 0.5, 
                  right = 0, 
                  top = 0.65) +                   
    inset_element(p = umap_img, 
                  left = 1.3, 
                  bottom = 0.3, 
                  right = 0, 
                  top = 0.5) +
    inset_element(p = tsne_30_img, 
                  left = 0.41, 
                  bottom = 0.03, 
                  right = 0, 
                  top = 0.23)
